\renewcommand\bibname{References}
\begin{thebibliography}{9}

\bibitem{ArchettiSperanzaVigo} 
C. Archetti, M.G. Speranza, D. Vigo.
\textit{Vehicle Routing Problems with Profits.} 
Department of Economics and Management, University of Brescia, Italy 2013

\bibitem{ArchettiHertzSperanza} 
C. Archetti, A. Hertz, and M.G. Speranza.
\textit{Metaheuristics for the team orienteering problem.} 
Journal of Heuristics, 13:49–76, 2007.

\bibitem{BoulyDangMoukrim} 
H. Bouly, D.-C. Dang, and A. Moukrim.
\textit{A memetic algorithm for the team orienteering problem.}
4OR, 8:49–70, 2010.

\bibitem{ButtCavalier} 
S.E. Butt and T.M. Cavalier.
\textit{A heuristic for the multiple tour maximum collection problem.}
Computers and Operations Research, 21:101–111, 1994.

\bibitem{ButtRyan} 
S.E. Butt and D.M. Ryan.
\textit{An optimal solution procedure for the multiple tour maximum collection problem using column generation.}
Computers and Operations Research, 26:427–441, 1999.

\bibitem{ChaoGoldenWasil} 
I-M. Chao, B.L. Golden, and E.A. Wasil.
\textit{The team orienteering problem.}
European Journal of Operational Research, 88:464–474, 1996.

\bibitem{GoldenLaporteTaillard} 
Golden B, Laporte G, Taillard E.
\textit{An adaptive memory heuristic for a class of vehicle routing problems with minmax}
Computers and Operations Research 1997;24:445–52.

\bibitem{DangGuibadjMoukrim} 
D.-C. Dang, R.N. Guibadj, and A. Moukrim.
\textit{A PSO-based memetic algorithm for the team orienteering problem.}
In C. Di Chio, A. Brabazon, G. Di Caro, R. Drechsler, M. Farooq, J. Grahl, G. Greenfield, C. Prins, J. Romero, G. Squillero, E. Tarantino, A. Tettamanzi, N. Urquhart, and A. Uyar, editors, Applications of Evolutionary Computation, Lecture Notes in Computer Science, pages 471–480. Springer, Berlin, 2011.

\bibitem{goldenlevyvohra} 
B.L. Golden, L. Levy, and R. Vohra.
\textit{The orienteering problem.}
Naval Research Logistics, 34:307–318, 1987.

\bibitem{KeArchettiFeng} 
L. Ke, C. Archetti, and Z. Feng.
\textit{Ants can solve the team orienteering problem.}
Computers and Industrial Engineering, 54:648–665, 2008.

\bibitem{SouffriauVansteenwegenBergheOudheusden} 
W. Souffriau, P. Vansteenwegen, G. Vanden Berghe, and D. Van Oudheusden.
\textit{A path relinking approach for the team orienteering problem.}
Computers and Operations Research, 37:1853–1859, 2010.

\bibitem{TangMillerHooks} 
H. Tang and E. Miller-Hooks.
\textit{A tabu search heuristic for the team orienteering problem.}
Computers and Operations Research, 32:1379–1407, 2005.

\bibitem{VansteenwegenSouffriauBergheOudheusden} 
P. Vansteenwegen, W. Souffriau, G. Vanden Berghe, and D. Van Oudheusden.
\textit{A guided local search metaheuristic for the team orienteering problem.}
European Journal of Operational Research, 196:118–127, 2009.

\bibitem{Goldberg} 
Goldberg, D.
\textit{Genetic algorithms in search, optimization and machine learning.}
1st Ed., Addison-Wesley, Massachusetts, 1989.

\bibitem{Bean} 
Bean, J.C.
\textit{Genetic algorithms and random keys for sequencing and optimization.}
ORSA J. Comput. 6, 154–160 (1994)

\bibitem{SpearsDeJong} 
Villiam M. Spears , Kenneth A. De Jong
\textit{On the virtues of parameterized uniform crossover.}
1991

\bibitem{BallouChowdhury} 
Ballou, R., Chowdhury, M.
\textit{MSVS: An extended computer model for transport mode selection. The Logistics and Transportation.}
1980

\bibitem{BoussierFeilletGendreau} 
S. Boussier, D. Feillet, and M. Gendreau.
\textit{An exact algorithm for the team orienteering problem.}
5:211–230, 2007.

\bibitem{SouffriauVansteenwegenBergheOudheusden} 
W. Souffriau, P. Vansteenwegen, G. Vanden Berghe, and D. van Oudheusden
\textit{A greedy randomized adaptive search procedure for the team orienteering problem}
Proceedings of the 9th EU/Meeting on Metaheuristics for Logistics and Vehicle Routing, Troyes, France, October 2008.

\bibitem{FerreiraQuintasOliveiraPereiraDias} 
Jo~ao Ferreira, Artur Quintas, José A. Oliveira, Guilherme A.B. Pereira, and Luis Dias
\textit{Solving the team orienteering problem}
Universidade do Minho, Braga, Portugal, 2012

\bibitem{ZettamElbenani} 
Manal Zettam, Bouazza Elbenani
\textit{A novel Randomized Heuristic for the Team Orienteering Problem}
Mohammed V University Rabat, Morocco, 2016

\bibitem{IntancesChaoTsiligirides} 
Fuente donde encontré las intancias de problemas de Chao y Tsiligirides
\\\texttt{https://www.mech.kuleuven.be/en/cib/op\#section-3}

\bibitem{Croes} 
Croes GA
\textit{A Method for Solving Travelling-Salesman Problems.}
Operations Research, Vol. 6, No. 6, pp. 791-812, (1958).

\end{thebibliography}